%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Keith Low} \\ \vspace{1pt}
    \small +65 8908 3135 $|$ \href{mailto:keith_low@mymail.sutd.edu.sg}{\underline{keith\_low@mymail.sutd.edu.sg}} $|$ 
    \href{https://linkedin.com/in/keith-lwk}{\underline{linkedin.com/in/keith-lwk}} $|$
    \href{https://github.com/keeve101}{\underline{github.com/keeve101}}
\end{center}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AI Engineer}{Jan. 2024  -- Jul. 2024}
      {Hyundai Motor Group Innovation Center Singapore (HMGICS)}{Singapore}
      \resumeItemListStart
        \resumeItem{Developed a novel chat message disentanglement pipeline using LLMs for efficient annotation}
        \resumeItem{Implemented a Retrieval-Augmented Generation (RAG) system for domain-specific Question-Answering (QA), including data pre-processing, vector database integration, and evaluation}
      \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Teaching Assistant}{Sep. 2022  -- Dec. 2022}
      {Singapore University of Technology and Design}{Singapore}
      \resumeItemListStart
        \resumeItem{Crafted fundamental programming questions in Python to facilitate understanding of Computer Science concepts}
        \resumeItem{Collaborated with course instructor to provide support to students, offering one-on-one assistance and explanations}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{LLMContextViz} $|$ \emph{Python, Explanability, Visualization, User Studies}}{Feb. 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Investigating LLM context windows and the challenges of context overflow on model performance}
            \resumeItem{Conducting user studies to understand how users interact with LLM context windows in common use cases}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Personal LLM Chat Application} $|$ \emph{Python, C++, QLoRA}}{Oct. 2023 -- Nov. 2023}
          \resumeItemListStart
            \resumeItem{Developed generative AI application utilizing a finetuned LLM to perform basic personal introduction and have short conversations}
            \resumeItem{Finetuned a quantized 7B parameter large-language model using quantized LoRA finetuning approach}
            \resumeItem{Created and utilized Python bindings to C++ low-level API given by llama.cpp library to run inferences locally}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{IoT Air Conditioner Controller System} $|$ \emph{Java, C, Android Studio, Arduino API}}{Jan. 2023 -- Apr. 2023}
          \resumeItemListStart
            \resumeItem{Worked in a team to develop an app to allow users to control their air conditioners remotely}
            \resumeItem{Utilized Java, Android Studio to develop the app with Firebase database backend, C for bridging MCU}
            \resumeItem{Awarded SUTD x Singtel Merit Award for the project}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Food Security Indicator Estimator Model} $|$ \emph{Python, NumPy, Matplotlib, Git}}{Sep. 2022 -- Dec. 2022}
          \resumeItemListStart
            \resumeItem{Developed a food security indicator estimator linear regression model to provide a low-cost early estimator of food security across nations based on the Global Food Security Index}
            \resumeItem{Achieved Best Project for the term's multi-disciplinary design challenge}
          \resumeItemListEnd
          
          \resumeProjectHeading
          {\textbf{Image Processing for Bluetooth Thermal Printer} $|$ \emph{C, Arduino API}}{Jan. 2022 -- Apr. 2022}
          \resumeItemListStart
            \resumeItem{Implemented image processing algorithm to decode snapshots captured from microcontroller, conversion into dithered formats for print through Bluetooth thermal printer}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Singapore University of Technology and Design}{Singapore}
      {Bachelor of Engineering in Computer Science and Design}{Sep. 2021 -- May 2025}
      \resumeItemListStart
        \resumeItem{4.57/5.0 GPA}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%
%-----------EXTRA-CURRICULARS-----------
\section{Extra-Curricular Activities}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Climbers Club President }{Jan. 2022  -- Jan. 2023}
      {Singapore University of Technology and Design}{Singapore}
      \resumeItemListStart
        \resumeItem{Led committee planning and climbing activities, directed club-related activities in school-wide events}
      \resumeItemListEnd
    \resumeSubheading
      {Rotaract Club Member}{Nov. 2021  -- Aug. 2022}
      {Singapore University of Technology and Design}{Singapore}
      \resumeItemListStart
        \resumeItem{Served as an educational mentor through YEAH! program, volunteering to teach and offer free tuition to underprivileged primary school children at local community center}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL, JavaScript/TypeScript, HTML/CSS} \\
     \textbf{Frameworks}{: React, Node.js, Vite.js, Express.js} \\
     \textbf{Tools}{: Git, GitHub, VS Code, Android Studio, Agile, MongoDB} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, ctypes, PyTorch, Transformers, PEFT}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
